### 2024-06-08 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

>>>>

load(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\adonisBac.RData)')
load(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\adonisArg.RData)')
load(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\adonisPwy.RData)')
adonisBac2$Microbiome = 'Bacteria'
adonisArg2$Microbiome = 'ARG'
adonisPwy2$Microbiome = 'Pathway'
adonisBac2$Variable = xs_norm[adonisBac2$variable]
adonisBac2$Variable %<>% factor(., levels = adonisBac2$Variable[order(adonisBac2$adonis.r2)])
adonisBac2$adonis.r2 %<>% as.numeric()
adonisBac2$adonis.p  %<>% as.numeric()
bbp = ggplot(adonisBac2, aes(x=adonis.r2, y=Variable)) +
  geom_col(fill="gray", width = 0.25, alpha = 0.8) +
  geom_point(aes(fill = adonis.p), stroke = 0.2, shape = 21, size = 5) +
  scale_fill_distiller(palette = 4, name = expression(~ italic(P) ~ 'value')) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), breaks = seq(0,0.1,0.02)) +
  theme(strip.text = element_text(size = 13), strip.background = element_rect(fill = '#E2E5E9', color = NA),
                   # axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
                   legend.position = 'right') +
  xlab(expression(italic(R)^2)) + ylab("") 
print(bbp)
adonisArg2$Variable = xs_norm[adonisArg2$variable]
adonisArg2$Variable %<>% factor(., levels = adonisArg2$Variable[order(adonisArg2$adonis.r2)])
adonisArg2$adonis.r2 %<>% as.numeric()
adonisArg2$adonis.p  %<>% as.numeric()
bbp = ggplot(adonisArg2, aes(x=adonis.r2, y=Variable)) +
  geom_col(fill="gray", width = 0.25, alpha = 0.8) +
  geom_point(aes(fill = adonis.p), stroke = 0.2, shape = 21, size = 5) +
  scale_fill_distiller(palette = 4, name = expression(~ italic(P) ~ 'value')) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), breaks = seq(0,0.1,0.02)) +
  theme(strip.text = element_text(size = 13), strip.background = element_rect(fill = '#E2E5E9', color = NA),
                   # axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
                   legend.position = 'right') +
  xlab(expression(italic(R)^2)) + ylab("") 
print(bbp)
adonisPwy2$Variable = xs_norm[adonisPwy2$variable]
adonisPwy2$Variable %<>% factor(., levels = adonisPwy2$Variable[order(adonisPwy2$adonis.r2)])
adonisPwy2$adonis.r2 %<>% as.numeric()
adonisPwy2$adonis.p  %<>% as.numeric()
bbp = ggplot(adonisPwy2, aes(x=adonis.r2, y=Variable)) +
  geom_col(fill="gray", width = 0.25, alpha = 0.8) +
  geom_point(aes(fill = adonis.p), stroke = 0.2, shape = 21, size = 5) +
  scale_fill_distiller(palette = 4, name = expression(~ italic(P) ~ 'value')) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), breaks = seq(0,0.1,0.02)) +
  theme(strip.text = element_text(size = 13), strip.background = element_rect(fill = '#E2E5E9', color = NA),
                   # axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
                   legend.position = 'right') +
  xlab(expression(italic(R)^2)) + ylab("") 
print(bbp)
adonis2DF = rbind(adonisBac2, adonisArg2, adonisPwy2) %>% as.data.frame()
sumDF = adonis2DF %>% group_by(Variable) %>%
  summarise(sum = sum( adonis.r2))
adonis2DF$Variable %<>% factor(., levels = sumDF$Variable[order(sumDF$sum)])
adonis2DF$Microbiome %<>% factor(., levels= c('Bacteria', 'Pathway', 'ARG'))
bpR = ggplot() +
  geom_bar(data = adonis2DF, mapping = aes(x=adonis.r2, y=Variable, fill = Microbiome), 
           position = "stack", stat = "identity",width=0.8) +
  scale_fill_manual(values = c('Bacteria' = '#F0D490', 'Pathway' = '#80B1D3', 'ARG' = '#99CCCC')) +
  scale_x_continuous(limits = c(0, 0.15), expand = expansion(mult = c(0,0)), breaks = seq(0,0.15,0.025)) +
  geom_text(data = sumDF, mapping = aes(x = sum+0.002, y = Variable, label = Variable), 
            size = 4.5, hjust = 0) +
  labs(x = expression(~~Adonis~~italic(R)^2)) +
  theme(legend.position = 'right', axis.text.y = element_blank(), axis.title.y = element_blank())
pdf('./adonis_barplot.pdf', width = 5.56, height = 3.49)
print(bpR)
dev.off()
adonis2DF$P = adonis2DF$adonis.p
adonis2DF$P[adonis2DF$P >= 0.05] = 1
adonis2DF$P[which(adonis2DF$P < 0.05)] = 0
pMat = reshape2::dcast(adonis2DF, Microbiome ~variable) %>% data.frame(., row.names = 1) %>% t()
row.names(pMat) = xs_norm[row.names(pMat)]
pMat = pMat[match(levels(adonis2DF$Variable) %>% rev(), row.names(pMat)), ]
pdf('./adonis_heatmap.pdf', width = 8.79, height = 6)
pheatmap(pMat, scale = F, cluster_cols = F, cluster_rows = F, border_color = 'white',
         cellwidth = 25,cellheight= 25, gaps_col = 1:2, gaps_row = 1:12,
         color = colorRampPalette(c('#CD5C5C', 'white'))(100))
dev.off()
